### 2015-02-11 doc/thesis/system.tex
Updating type system appendix to include the projection environment

We also use the tags \emph{unique}, \emph{open}, \emph{closed}, and
\emph{regular} to classify table types.
The tag \emph{unique} represents tables with no keys that do not
inhabit one of the table's key types, and with no alias.
In particular, the type of the table constructor has this tag.
The tag \emph{open} represents \emph{unique} table types that
have at least one alias.
The tag \emph{closed} represents \emph{unique} table types
that may have aliases.
In particular, the type of a class has this tag.
The tag \emph{regular} represents table types that do not provide
any guarantees about keys with types not listed in the table type.
In particular, in the concrete syntax, type annotations, interface
declarations, and userdata declarations always describe \emph{regular} table types.
In the next sections we explain in more detail why we need
different table types.

@@

The subtyping rule for function types is also standard:
\[
\begin{array}{c}
\mylabel{S-FUNCTION}\\
\dfrac{\senv \vdash s_{2} \subtype s_{1} \;\;\;
       \senv \vdash r_{1} \subtype r_{2}}
      {\senv \vdash s_{1} \rightarrow s_{1} \subtype s_{2} \rightarrow r_{2}}
\end{array}
\]

@@

The type $\Void$ is a subtype of itself and of a variadic type:
\[
\begin{array}{c}
\mylabel{S-VOID}\\
\senv \vdash \Void \subtype t{*}
\end{array}
\]

A variadic type $t{*}$ represents a sequence of values of type
$t \cup \Nil$, and the rule \textsc{S-VOID} handles the case where
a given sequence is empty.

>>>>

We also use the tags \emph{unique}, \emph{open}, \emph{closed}, and
\emph{regular} to classify table types.
The tag \emph{unique} represents tables with no keys that do not
inhabit one of the table's key types, and with no alias.
In particular, the type of the table constructor has this tag.
The tag \emph{open} represents \emph{unique} table types that
have at least one alias.
The tag \emph{closed} represents either \emph{unique} or \emph{open}
table types that do not allow inserting new keys. 
In particular, the type of a class has this tag.
The tag \emph{regular} represents table types that do not provide
any guarantees about keys with types not listed in the table type.
In particular, in the concrete syntax, type annotations, interface
declarations, and userdata declarations always describe \emph{regular} table types.
In the next sections we explain in more detail why we need
different table types.

@@

The subtyping rule for function types is also standard:
\[
\begin{array}{c}
\mylabel{S-FUNCTION}\\
\dfrac{\senv \vdash s_{3} \subtype s_{1} \;\;\;
       \senv \vdash s_{2} \subtype s_{4}}
      {\senv \vdash s_{1} \rightarrow s_{2} \subtype s_{3} \rightarrow s_{4}}
\end{array}
\]

@@

The type $\Void$ is a subtype of itself and of a variadic type:
\[
\begin{array}{c}
\mylabel{S-VOID2}\\
\senv \vdash \Void \subtype t{*}
\end{array}
\]

A variadic type $t{*}$ represents a sequence of values of type
$t \cup \Nil$, and the rule \textsc{S-VOID2} handles the case where
a given sequence is empty.
